Impact of switching bug trackers: a case study on a medium-sized open source project

### 2019-03-05 article/article.tex
Fix URL to GitHub repository.

All the data for this study was extracted on January 17\textsuperscript{th}, 2019 using the GitHub GraphQL API \cite{github_graphql_API}. Using this API allows to do large requests (100 nodes in a single request) with just the information we need (thus both reducing the bandwidth usage and speeding up the extraction process). We provide the extracted data as CSV files and a Jupyter notebook\footnote{Available at \url{https://github.com/Zimmi48/github-migration-analysis}.} with the code to request this data from GitHub, to load the CSV files, to run the pre-processing steps, and the analyses.%, and the robustness checks.

@@

The highest peak is in 2015, after the first beta release of version
8.5. This was the first release in more than two years and it
contained five big new features (``the result of five specific
long-term projects''\footnote{Quote from
  \url{https://coq.inria.fr/distrib/V8.9.0/refman/credits.html\#credits-version-8-5}. The
  next quotes are coming from the following sections of the same
  chapter of the Coq reference manual.}). Stabilizing these features
and their (unplanned) interactions required more than a year of
testing and three beta releases. The 8.5 release was both hard on
developers, who found the release cycle too long, and on users, who
were impacted by many compatibility issues. Consequently, a different
approach was taken for the following releases: versions 8.6, 8.7 and
8.8 were ``developed on a time-based development cycle'' and contain
``the result of refinements, stabilization of features and cleanups of
the internals of the system along with a few new features''. Attention
was given to regression testing: changes were systematically tested by
building a selection of the largest Coq projects. Therefore, it is not
surprising that these frequent releases are correlated to smaller
peaks of new bug reports.

@@

\scriptsize
%\paragraph{}
\noindent \footnotesize{\textbf{Supporting data.}}
We provide our extraction and analysis code as a Jupyter notebook and the data we used as CSV files. We also provide the XML export of Bugzilla that was used for the migration and the migration script. Everything is available from \url{https://github.com/Zimmi48/github-migration-analysis}.
%\paragraph{}

>>>>

All the data for this study was extracted on January 17\textsuperscript{th}, 2019 using the GitHub GraphQL API \cite{github_graphql_API}. Using this API allows to do large requests (100 nodes in a single request) with just the information we need (thus both reducing the bandwidth usage and speeding up the extraction process). We provide the extracted data as CSV files and a Jupyter notebook\footnote{\url{https://github.com/Zimmi48/impact-of-switching-bug-trackers}.} with the code to request this data from GitHub, to load the CSV files, to run the pre-processing steps, and the analyses.%, and the robustness checks.

@@

The highest peak is in 2015, after the first beta release of version 8.5. This was the first release in more than two years and it contained five big new features (``the result of five specific long-term projects''\footnote{Quote from:\\ \url{https://coq.inria.fr/distrib/V8.9.0/refman/credits.html\#credits-version-8-5}\\
The next quotes are coming from the following sections of the same chapter of the Coq reference manual.}). Stabilizing these features and their (unplanned) interactions required more than a year of testing and three beta releases. The 8.5 release was both hard on developers, who found the release cycle too long, and on users, who were impacted by many compatibility issues. Consequently, a different approach was taken for the following releases: versions 8.6, 8.7 and 8.8 were ``developed on a time-based development cycle'' and contain ``the result of refinements, stabilization of features and cleanups of the internals of the system along with a few new features''. Attention was given to regression testing: changes were systematically tested by building a selection of the largest Coq projects. Therefore, it is not surprising that these frequent releases are correlated to smaller peaks of new bug reports.

@@

\scriptsize
%\paragraph{}
\noindent \footnotesize{\textbf{Supporting data.}}
We provide our extraction and analysis code as a Jupyter notebook and the data we used as CSV files. We also provide the XML export of Bugzilla that was used for the migration and the migration script. Everything is available from \url{https://github.com/Zimmi48/impact-of-switching-bug-trackers}.
%\paragraph{}
